Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations

### 2021-01-06 README.Rmd
working on updating the readme

- information about the files in the repository,
- instructions for knitting the manuscript,
- descriptions of the bullet data used in the manuscript, and
- information on the font sizes used for the figures in the manuscript.

@@

- [bullet-train.csv.zip](data/bullet-train.csv.zip) and [bullet-test.csv.zip](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [raw](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
  - [CCFs_withlands.csv.zip](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [h224-set1-features.rds.zip](data/raw/h224-set1-features.rds.zip) and [h224-set11-features.rds.zip](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [readme.txt](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

@@

- [figure-08-1.png.zip](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
- [figure-readme.png](figure-static/figure-readme.png) is a figure used in this readme.

@@

[**submission**](submission)

Contains the files submitted to the ASA Data Science Journal. These files are moved to this folder using code in the file [code/03-submission-steps.R](code/03-submission-steps.Rmd). The only submission files not included on GitHub are the EPS figures due to size constraints.

@@

- [.gitignore](.gitignore) contains objects to be ignored by git.
- [paper.Rnw](paper.Rnw), [paper.pdf](paper.pdf), and [paper.tex](paper.tex) are the manuscript. Note that paper.pdf and paper.tex are generated by paper.Rnw.
- [README.Rmd](README.Rmd) and [README.md](README.md) are the readme files that generated this output.
- [references.bib](references.bib) contains the bibtex information for the references in the manuscript.
- [WileyNJG-AMS.bst](WileyNJD-AMS.bst) and [WileyNJG-v2.cls](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.

>>>>

- [information about the files in the repository](#description-of-items-in-repository),
- [instructions for knitting the manuscript](#instructions-for-compiling-manuscript),
- [descriptions of the bullet data used in the manuscript](#additional-information-on-bullet-data), and
- [information on the font sizes used for the figures in the manuscript](#figure-font-size-information).

@@

- [bullet-rf.rds](data/bullet-rf.rds) contains the saved version of the random forest trained using the bullet matching training data.
- [bullet-test.csv.zip](data/bullet-test.csv.zip) and [bullet-train.csv.zip](data/bullet-train.csv.zip) contain the data used for the bullet examples in the manuscript. See ["Additional Information on Bullet Data"](#additional-information-on-bullet-data) below for more information about the data.
- [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [raw](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
  - [CCFs_withlands.csv.zip](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [h224-set1-features.rds.zip](data/raw/h224-set1-features.rds.zip) and [h224-set11-features.rds.zip](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [readme.txt](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
- [sine-data-test.rds](data/sine-data-test.rds) and [sine-data-train.rds](data/sine-data-train.rds) contain saved version of the sine data testing and training sets generated by the code in the manuscript.
- [sine-lime-explain.rds](data/sine-lime-explain.rds) contains the LIME explanations for the random forest predictions from the sine data test set.

@@

- [figure-06-1.png.zip](figure-static/figure-06-1.png.zip) is the one figure in the manuscript that is not generated using R code.
- [figure-readme.png](figure-static/figure-readme.png) is a figure used in this readme.

@@

[**submission**](submission/)

Contains folders with the files submitted to the ASA Data Science Journal. The folders within are named by the date of submission. The files are moved here using code in the file [code/03-submission-steps.R](code/03-submission-steps.Rmd). The only submission files not included on GitHub are the EPS figures due to size constraints.

[**support-info**](support-info/)

Contains the files associated with the manuscript's supporting information document:

- [figures](support-info/figures) contains the figures generated by the supporting information document.
- [support-info-references.bib](support-info/support-info-references.bib) contains the bibtex information for the references in the supporting information document.
- [supporting-information.pdf](support-info/supporting-information.pdf) and [supporting-information.Rnw](support-info/supporting-information.Rnw) are the supporting information document.

@@

- [.gitattributes](.gitattributes) is needed for GitHub large file storage.
- [.gitignore](.gitignore) contains objects to be ignored by git.
- [paper.Rnw](paper.Rnw), [paper.pdf](paper.pdf), and [paper.tex](paper.tex) are the manuscript. Note that paper.pdf and paper.tex are generated by paper.Rnw.
- [README.Rmd](README.Rmd) and [README.md](README.md) are the readme files that generated this output.
- [references.bib](references.bib) contains the bibtex information for the references in the manuscript.
- [WileyNJG-AMS.bst](WileyNJD-AMS.bst) and [WileyNJG-v2.cls](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.
